\cvsection{Work Experience}

\begin{cventries}
  \cventry
    {Expert Software Engineer}
    {Mercedes-Benz, Daimler}
    {Berlin, Germany}
    {August 2020 - Present}
    {
      \begin{cvitems}
        \item {Development of Adaptive AUTOSAR standard platform components for networking control units for infotainment and ADAS ECUs.}
        \item {Devlopment of virtual environment for Automotive Ecosystem enabling simulation of signal and service exchange between different ECUs.}
        \item {Evaluation of safety concepts and architectures as part of the overall system requirements with processes specified by functional safety standard ISO26262}
      \end{cvitems}
    }	

  \cventry
    {System Engineer}
    {1und1, IONOS}
    {Berlin, Germany}
    {June 2018 - August 2020}
    {
      \begin{cvitems}
        \item {Assist in developing core virtualization features and stronger QEMU support for x86 virtualization, such as improving migration, virtio and debugging features.Assist other team members in developing and upstreaming changes to QEMU and the Linux kernel.}
      \end{cvitems}
    }	

  \cventry
    {System Engineer}
    {Nvidia}
    {Hyderabad, INDIA}
    {Mar 2017 - June 2018 }
    {
      \begin{cvitems}
        \item {Develop HAL layer and drivers for NVDLA(Nvidia Deep Learnin Accelerator ) to accelerate computational tasks, such as machine learning, engineering workloads, and scientific computing on Nvidia Tegra ARM chipset.}
        \item {Added support for multiple GPUs, dGPU and host memory allocations getting shared between GPUs.}
        \item {Added support for user-mode API interfaces and libraries necessary of host applications to launch compute kernels to CUDA kernel agents.}
      \end{cvitems}
    }	
    
  \cventry
    {Senior Software Engineer}
    {Aricent, Altran}
    {Gurgaon, India}
    {Jan 2015 - Feb 2017}
    {
      \begin{cvitems}
        \item {Developed a highly accurate prototype of Action Camera Device with 3D Capture Mapping, pattern recognition and object detection from captured scenes using Caffe over TensorRT.}
        \item {Integrated with display stack supporting 2D 3D graphics over Linux Android HAL.}
        \item {Panel bring-up for MIPI DSI and eDP with multiple vendors like Novatek, LG, Sharp, Panasonic etc.}
        \item {Ported OpenCore based OpenMax (OMX) codecs for accelerated decoding.}
      \end{cvitems}
    }	  
	  
  \cventry
    {Software Engineer}
    {Safenet, Gemalto}
    {Noida, India}
    {Dec 2013 - Jan 2015}
    {
      \begin{cvitems}
        \item {Porting proprietary Encryption Linux Filesystem Driver the filesystem driver to newer kernel versions.}
        \item {Development of container based build system for building the driver on different Linux distros simultaneously and package them in a single rpm/deb.}
        \item {Responsible for Debugging file system issues and Bug fixes and verification.}
      \end{cvitems}
    }	  
	  
  \cventry
    {Software Engineer}
    {AE Telelink Systems}
    {New Delhi, India}
    {Jan 2012 - Dec 2013}
    {
      \begin{cvitems}
        \item {Developed firmware for Voice Logger product used for storing audio data. Developed FAT file system enabling logging of voiced calls in MP3 format.}
      \end{cvitems}
    }  
\end{cventries}
